`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-19 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the convolution and inner product of two Gaussian

@@

\section{Notation}

>>>>

\begin{equation}\label{eq:FTofGaussian}

@@

\section{Convolution and inner product of two $n$-dimensional Gaussian basis functions}\label{ap:ConvandIn}
Consider two Gaussian basis functions
 \phi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
\phi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right)
First we derive the convolution of two Gaussian basis functions assuming $\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$. Convolution theorem states that the Fourier transform of a convolution is the product of Fourier transforms. Using equation \ref{eq:FTofGaussian} we have
\boldsymbol\Phi_i(\boldsymbol\nu)\boldsymbol\Phi_j(\boldsymbol\nu)&=&\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
taking the inverse Fourier transform we can write the convolution as
\begin{equation}\label{eq:ConvoftwoGaussian}
 (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
 (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
where $\boldsymbol\mu=\mu_i+\mu_j$.

The inner product of two Gaussian basis functions is defined as
\begin{equation}\label{eq:InofGaussianDefinition}
\phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r
\end{equation}
A Gaussian basis function is symmetric with respect to its center, therefore
\begin{equation}\label{eq:GaussianSymmetry}
 \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r)
\end{equation}
A direct consequence of equation \ref{eq:GaussianSymmetry} is
\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
 \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r)
\end{equation}
substituting equation \ref{eq:ConsequenceofGaussianSymmetry} in equation \ref{eq:InofGaussianDefinition} we have 
\begin{eqnarray}
\phi_i\otimes\phi_j&=&\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathcal R^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i)
\end{eqnarray}
from equation \ref{eq:ConvoftwoGaussianNonzeroMean} we have
\begin{equation}
 \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
\end{equation}
\section{Notation}
